Baseline centering problem

### 2018-12-12 paper/tangotd.tex

Therefore, by various combinations of actual and simulated transitions,
we can easily compute samples of
\begin{equation}
\tfrac12 \transp{\Phi}(\transp{\Delta}\rho \tilde \Delta+\transp{\tilde
\Delta}\rho\Delta)V
-
\transp{\Phi}\transp{\tilde \Delta}
\rho R
\end{equation}
(variant 1) and
\begin{equation}
\tfrac12 \transp{\Phi}\transp{\Delta}
\rho(\tilde \Delta V-R)
+
\tfrac12 \transp{\Phi}\transp{\tilde \Delta}
\rho(\Delta V-R)
\end{equation}
(variant 2, under the conditions of the footnote).
Setting
\begin{equation}
C\deq \tfrac12 (\transp{\Delta}\rho \tilde \Delta+\transp{\tilde
\Delta}\rho\Delta)
\end{equation}
variant 1 is the gradient of
\begin{equation}
\norm{V-C^{-1}\transp{\tilde\Delta}\rho R}^2_C
\end{equation}
while variant 2 is the gradient of
\begin{equation}
\norm{V-\frac12 C^{-1}(\transp{\tilde\Delta}+\transp{\Delta})\rho R}^2_C
\end{equation}

@@

The fixed point $\hat V_1$ for variant 1 has less clear an
interpretation. Defining the matrix $\eps$ via $\Delta \eqd(\Id+\eps\rho)\tilde \Delta$ where
$\eps$ is some hopefully small model error, we find
\begin{align}
\hat V_2&=C^{-1}\transp{(\rho\tilde \Delta)}R
\\&=\left(
\Delta+\frac{(\transp{(\rho\tilde \Delta)})^{-1}\transp{\Delta} \rho \tilde
\Delta-\Delta}{2}
\right)^{-1}R
\\&=\left(
\Delta+\frac12(\transp{\eps}-\eps)\rho\tilde \Delta
\right)^{-1}R
\end{align}
In particular, if $\eps$ is symmetric the error vanishes, but if $\eps$
is antisymmetric we end up computing $\tilde \Delta^{-1}R$, namely the
Bellman function of the model. Usually $\eps$ would be somewhere in
between; I do not know if it is possible to force the model to favor
symmetric values of $\eps$.

>>>>

Therefore, by various combinations of actual and simulated transitions,
we can easily compute samples of
\begin{equation}
\tfrac12 \transp{\Phi}(\transp{\Delta}\rho \tilde \Delta+\transp{\tilde
\Delta}\rho\Delta)V
-
\transp{\Phi}\transp{\tilde \Delta}
\rho R
\end{equation}
(variant 1) and
\begin{equation}
\tfrac12 \transp{\Phi}\transp{\Delta}
\rho(\tilde \Delta V-R)
+
\tfrac12 \transp{\Phi}\transp{\tilde \Delta}
\rho(\Delta V-R)
\end{equation}
(variant 2, under the conditions of the footnote). Variant 2 corresponds
to fully symmetrizing the roles of the synthetic and real samples in
two-sampling.

Setting
\begin{equation}
C\deq \tfrac12 (\transp{\Delta}\rho \tilde \Delta+\transp{\tilde
\Delta}\rho\Delta)
\end{equation}
variant 1 is the gradient of
\begin{equation}
\norm{V-C^{-1}\transp{\tilde\Delta}\rho R}^2_C
\end{equation}
while variant 2 is the gradient of
\begin{equation}
\norm{V-\frac12 C^{-1}(\transp{\tilde\Delta}+\transp{\Delta})\rho R}^2_C
\end{equation}

@@

The fixed point $\hat V_1$ for variant 1 has less clear an
interpretation. Define the matrix $\eps$ via $\Delta \eqd(\Id+\eps\rho)\tilde \Delta$ where
$\eps$ is some hopefully small model error. Then
\begin{align}
\hat V_2&=C^{-1}\transp{(\rho\tilde \Delta)}R
\\&=\left(
\Delta+\frac{(\transp{(\rho\tilde \Delta)})^{-1}\transp{\Delta} \rho \tilde
\Delta-\Delta}{2}
\right)^{-1}R
\\&=\left(
\Delta+\frac12(\transp{\eps}-\eps)\rho\tilde \Delta
\right)^{-1}R
\end{align}
In particular, if $\eps$ is symmetric the error vanishes, but if $\eps$
is antisymmetric we end up computing $\tilde \Delta^{-1}R$, namely the
Bellman function of the model. Usually $\eps$ would be somewhere in
between; I do not know if it is possible to force the model to favor
symmetric values of $\eps$.
